\documentclass{40k}

%%-- For cards
\pgfmathsetmacro{\cardroundingradius}{2mm}
\pgfmathsetmacro{\striproundingradius}{1mm}
\pgfmathsetmacro{\ruleheight}{0.1}
\pgfmathsetmacro{\stripwidth}{1.1}
\pgfmathsetmacro{\stripheight}{1.1}
\pgfmathsetmacro{\strippadding}{0.1}
\pgfmathsetmacro{\textpadding}{0.3}
\newcommand{\stripcolor}{black}
%%-------

\input{covertcard}

\begin{document}
\squelchbackground%

\noindent%
\covertcard%
{Sabotage}%
{You've been sent behind enemy lines to cut power lines, destroy
  equipment, and place boobytraps.}%
{After all deployment, secretly select a piece of terrain wholely
  within your opponent's deployment zone.  Treating it as an objective
  marker for which (only) Elite and Fast Attack units have Objective
  Secured, you succeed if you control it at the end of any of your
  turns after the first.}%
{Your alliance gains half the maximum victory points possible this
  match and your choice of installations has no effect until the end
  of the next round.}  \hfill%
\covertcard%
{Interrogation}%
{Command has ordered you to capture and interrogate prisoners.  It's
  against your usual ``No mercy'' philosophy, but they're in charge.}%
{After all deployment, secretly select an enemy character (independent
  or otherwise).  You succeed if that character is removed as a
  casualty and you pass a~D6 test against its role:

\bigskip
\begin{minipage}{1.0\linewidth}\centering
\textbf{HQ} 2+ ~~ \textbf{Elite} 3+ ~~ \textbf{Troop} 5+\\
\textbf{Fast} 4+ ~~ \textbf{Heavy} 4+  
\end{minipage}}%
{Your alliance gains half the maximum victory points possible this
  match and your opponent's alliance must reveal their strategic
  campaign session objective.}

\clearpage

\noindent%
\covertcard%
{Sweep \& Scan}%
{Your troops are on the roll, rapidly covering ground in the hunt for
  intel.  You might miss something moving so fast, but time's up.}%
{At the end of each of your turns beginning with Turn~2, secretly make
  a note for each primary objective marker outside your deployment
  zone which you control and have not previously controlled.  If by
  the end of the game you have controlled at least two at some point,
  you succeed.}%
{Your alliance pulls a search result for each continent on which a
  player achieved this mission as though it shared control.}

\vfill

\noindent%
\covertcard%
{Data Port}%
{You've detected an active, unsecured data port among the wreckage
  strewn about.  If you can hold it long enough, you might be able to
  extract something useful.}%
{After all deployment concludes, secretly select and record a primary
  objective marker outside your deployment zone.  You succeed if you
  control it at the end of your turn for any two turns in a row,
  excluding Turn~1.}%
{In addition to the points you earn as usual, your alliance gains half
  the maximum victory points possible for this match toward its
  overall and this continent.} \hfill%
\covertcard%
{Signals}%
{You're tracking an enemy HQ signal.  If you can triangulate it,
  you'll know where they're based.}%
{After all deployment concludes, secretly select and record a table
  quarter not on your table edge.  At game end if you have a scoring
  unit in that quarter and your opponent does not, you succeed.  Units
  with Objective Secured trump those without.}%
{In addition to the points you earn as usual, your alliance gains half
  the maximum victory points possible for this match toward its
  overall and this continent.}

\clearpage
\restorebackground%

\end{document}
